Generating Correlated Data for Omics Simulation

### 2025-05-05 manuscript/paper.qmd
Add supplemental document

```{r}
#| include: false
source("compare_to_real.R")
```

@@

```{r}
#| label: fig-compare-to-real
#| fig-cap: !expr glue::glue("Comparison to real data run on a mouse cortex data set from GSE151923. (a-b) Comparison of gene (a) mean expression and (b) variance, log-scaled in real and PCA simulated data. The line of equality is marked in black. Points are colored according to the density of points in their region. Wishart and corpcor methods give similar results (not shown). (c) Quantile-quantile plot comparing correlation values of gene pairs from real data and simulated data (both with and without dependence). Genes with at least {HIGH_EXPR_CUTOFF} reads were used. Values on the diagonal line indicate a match between the simulated and real data sets. (d) Projections onto the top two principal components of the real data set for both real and simulated data. All 8 simulations (96 samples for each simulation) shown. (e) Principal component analysis was performed on all data sets and the variance captured by the top components is shown. Unlike (d), these components were fit from each data set considered separately instead of reusing the weights from the real data.")
#| fig-width: 10
#| fig-height: 10
compare_to_real_plot
```

>>>>

@@

```{r}
#| label: fig-compare-to-real
#| fig-cap: "Comparison to real data run on a mouse cortex data set from GSE151923. (a-b) Comparison of gene (a) mean expression and (b) variance, log-scaled in real and PCA simulated data. The line of equality is marked in black. Points are colored according to the density of points in their region. Wishart and corpcor methods give similar results (not shown). (c) Quantile-quantile plot comparing correlation values of gene pairs from real data and simulated data (both with and without dependence). Genes with at least 100 reads were used. Values on the diagonal line indicate a match between the simulated and real data sets. (d) Projections onto the top two principal components of the real data set for both real and simulated data. All 8 simulations (96 samples for each simulation) shown. (e) Principal component analysis was performed on all data sets and the variance captured by the top components is shown. Unlike (d), these components were fit from each data set considered separately instead of reusing the weights from the real data."
#| fig-width: 10
#| fig-height: 10
readRDS("../processed/compare_to_real_plot.GSE151923.RDS")
```
